Asymmetric relationships and their effects on coexistence

### 2023-02-03 paper/Paper.Rnw
small things

%G2 
Fulfilling goal G2 of the Introduction (to explore, using the lottery model, the relative magnitudes 
of the contributions to coexistence that come from ATAs compared to other mechanisms), Fig.
\ref{fig:fig3} shows that the ATA term of (\ref{eq:full_decomp}) often, but not always, has 
magnitude comparable to the magnitudes of other terms of the extended MCT decomposition. 
Magnitudes of $\Delta_i^{[EC]}$ tended to be larger, relative to the magnitudes of the 
other terms of (\ref{eq:full_decomp}), for smaller-magnitude differences between $\mu_1$ and 
$\mu_2$, i.e., for closer-to-equal competitors. 
In the $\mu_1=\mu_2$ case (panels a-d), for which the two species were equal 
competitors, storage effects (blue plus red
lines on Fig. \ref{fig:fig3}) were the only means by which coexistence could occur, and ATA effects
tended to be negative, weakening total storage effects.

@@

%***DAN: I edited the caption (2023 01 26) but this is the completely the wrong figure. I need to replace it 
%with Jasmin's new pedagogical figure once I know where in the repo 
%structure that one is generated and stored, and after I have re-run Jasmin's code, and after she has made the
%changes I recently asked for (see next comment).
%***DAN: I asked Jasmin to replace the \phi with \varphi in the axis labels on b and d, and to make the marginals
%on b and c be *standard* normal instead of just normal.
\begin{figure}
\includegraphics[width=.75\textwidth]{../results_figs/fig2.pdf}
\caption{Illustration of how asymmetric tail associations are removed while retaining marginal distributions and correlation 
between variables (see Theory). (a) An example original bivariate distribution $(E_i,C_{i \bs i})$, with ATA present. 
(b) Marginals are now normalized. The variables $E_i$ and $C_{i \bs i}$ are individually transformed to have standard normal 
marginals through a composition of the inverse of the standard normal cumulative distribution function (CDF), 
$\varphi^{-1}$, and 
each variable's CDF, $F_{E_i}$ and $F_{C_{i \bs i}}$, respectively.  
(c) A newly generated bivariate normal distribution, $(e_i,c_{i \bs i})$, with correlation $\ddot{\rho}=\rho$
selected to match that of the original distribution (see Theory). (d) Two new variables, 
$E_i^{||}$ and  $C_{i \bs i}^{||}$,
%***DAN: I replaced \nat in the above two expressions by || because for some reason the \nat does not
%compile when it occurs within a caption. Not sure how to deal with that, but leaving it alone for now.
which have the same marginals and correlation as the original $E_i$ and $C_{i \bs i}$ variables of (a) but 
which have symmetric association structure. These variables are obtained by transforming the marginals from (c), 
$e_i$ and $c_{i \bs i}$, using the inverses of the functions used in (b).
For illustration purposes we started with beta distributed $E_i$ and $C_{i \bs i}$. Contour lines are 
$\log_{10}$ of probability density on all panels. 
\label{fig:pedagog2}}
\end{figure}

>>>>

%***DAN: made it to here, 2023 02 03, 4:11 pm. Resume from here.

%***DAN: copy of goal from the Intro
%G2) To explore, using the simple lottery model, the relative magnitudes of the contributions to coexistence that come
%from ATAs compared to other, previously known mechanisms of coexistence; and to determine whether species may 
%sometimes coexist with ATAs but not without, or vice versa.

%G2 
To begin fulfilling goal G2 of the Introduction (to explore, using the lottery model, the relative magnitudes 
of the contributions to coexistence that come from ATAs compared to other mechanisms; and to see if ATA rescue 
or ATA exclusion can occur), Fig.
\ref{fig:fig3} shows that the ATA term of (\ref{eq:full_decomp}) often, but not always, has 
magnitude comparable to the magnitudes of other terms of the extended MCT decomposition. 
Magnitudes of $\Delta_i^{[EC]}$ tended to be larger, relative to the magnitudes of the 
other terms of (\ref{eq:full_decomp}), for smaller-magnitude differences between $\mu_1$ and 
$\mu_2$, i.e., for closer-to-equal competitors. 
In the $\mu_1=\mu_2$ case (panels a-d), for which the two species were equal 
competitors, storage effects (blue plus red
lines on Fig. \ref{fig:fig3}) were the only means by which coexistence could occur, and ATA effects
tended to be negative, weakening total storage effects.

@@

%***DAN: This looks pretty good except the histograms for some marginals do not really look like the plotted
%pdfs of the marginals. I think Jasmin said in an email she was fixing this.
\begin{figure}
\includegraphics[width=1.025\textwidth]{../results_figs/theory_fig_col.pdf}
\caption{Illustration of how asymmetric tail associations are removed while retaining marginal distributions and correlation 
between variables (see Theory). (a) An example original bivariate distribution $(E_i,C_{i \bs i})$, with ATA present. 
(b) Marginals are now normalized. The variables $E_i$ and $C_{i \bs i}$ are individually transformed to have standard normal 
marginals through a composition of the inverse of the standard normal cumulative distribution function (CDF), 
$\varphi^{-1}$, and 
each variable's CDF, $F_{E_i}$ and $F_{C_{i \bs i}}$, respectively.  
(c) A newly generated bivariate normal distribution, $(e_i,c_{i \bs i})$, with correlation $\ddot{\rho}=\rho$
selected to match that of the original distribution (see Theory). (d) Two new variables, 
$E_i^{||}$ and  $C_{i \bs i}^{||}$,
%***DAN: I replaced \nat in the above two expressions by || because for some reason the \nat does not
%compile when it occurs within a caption. Not sure how to deal with that, but leaving it alone for now.
which have the same marginals and correlation as the original $E_i$ and $C_{i \bs i}$ variables of (a) but 
which have symmetric association structure. These variables are obtained by transforming the marginals from (c), 
$e_i$ and $c_{i \bs i}$, using the inverses of the functions used in (b).
For illustration purposes we started with beta distributed $E_i$ and $C_{i \bs i}$. Contour lines are 
$\log_{10}$ of probability density on all panels. 
\label{fig:pedagog2}}
\end{figure}
